---
title: "RMarkdown Gapminder exploration"
author: "Emma Graham"
date: "September 19, 2016"
output: 
  html_document:
    keep_md: yes
---

This is an R Markdown file that attempts to explore the Gapminder data.
First, let's install the package and inport it into R

Let's load the gapminder data and look at the first few rows and columns of the data
```{r}
library(gapminder)
head(gapminder)
```

Let's make a histogram of the life expectancy of all people included in the dataset. 

```{r}
hist(gapminder$lifeExp)
```

Let's look at how many individuals are from each continent

```{r}
summary(gapminder$continent)
```

Let's make a plot using ggplot2 that shows the relationship between country GDP and life expectancy. This was taken from Jenny Bryan's "care feeding data into R" html file on stat545.com

```{r}
library(ggplot2)
p <- ggplot(subset(gapminder, continent != "Oceania"),
            aes(x = gdpPercap, y = lifeExp))
p <- p + scale_x_log10() # log the x axis the right way
p + geom_point() # scatterplot
p + geom_point(aes(color = continent)) # map continent to color
p + geom_point(alpha = (1/3), size = 3) + geom_smooth(lwd = 3, se = FALSE)
p + geom_point(alpha = (1/3), size = 3) + facet_wrap(~ continent) +
  geom_smooth(lwd = 1.5, se = FALSE)
```